Auditory Scene Similarity Retrieval and Classification with Relevance based Quantization of Scattering Features

### 2016-12-12 paper/structureScene.tex
Edit abstract

This paper introduces a generic hierarchical modeling scheme for acoustic scenes using the wavelet scattering transform at sub-second timescales with relevance based quantization at larger timescales. Applying the proposed approach to the acoustic scene similarity retrieval and acoustic scene classification tasks on publicly available datasets using a state-of-the-art classifier demonstrates the potential of the features designed using the wavelet scattering transform, consistently outperforming a baseline of mel-frequency cepstral coefficients (MFCCs).

In addition, representing the scene at larger time scale as a set of representative features from coherent segments is an effective approach for acoustic scene similarity retrieval, as it is found that it allows the retrieval system to focus on discriminative features.
\end{abstract}

% Note that keywords are not normally used for peerreview paper.
\begin{IEEEkeywords}
acoustic scene classification, acoustic scene segmentation, scattering, wavelets
\end{IEEEkeywords}

>>>>

This paper introduces a generic hierarchical modeling scheme for acoustic scenes using the wavelet scattering transform at sub-second time-scales with relevance-based quantization at larger time-scales. Instead of representing a scene using summary statistics, a method popularized by bag-of-features models, each scene is represented by a subset of its most representative features, allowing the retrieval system to focus on particular discriminative features in the scene. We demonstrate the potential of the proposed approach for both acoustic scene similarity retrieval and acoustic scene classification tasks on publicly available datasets, consistently outperforming baseline mel-frequency cepstral coefficient (MFCC) methods.

\end{abstract}

% Note that keywords are not normally used for peerreview paper.
\begin{IEEEkeywords}
acoustic scene classification, acoustic scene segmentation, acoustic scene similarity retrieval, scattering, wavelets, invariance
\end{IEEEkeywords}
